Penalized linear mixed models for structured genetic data

### 2021-03-02 main.tex
Figures 5 and 6

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\caption{Precision recall curves across $\lambda$ values from the Empirical genome-wide analysis. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pc1_corr.png}
\caption{Pathwise absolute correlation of selected, non-causal SNPs with the first principal component (PC1) of the data in Empirical genome-wide analysis. Plotted line is the mean absolute correlation of all incorrectly selected SNPs for a particular $\lambda$ value, with shaded region indicating $\pm$ 1 SE. Single replication case study with $\eta = 0.5, \xi = 0.8$. \anna{get rid of 'Method' legend title.}}
\label{fig:gw_pc1_corr}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\includegraphics[scale = 0.9]{figures/genomewide_prc2.png}
\caption{Precision values for each method and number of selected SNPs from the Empirical genome-wide analysis. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}
\anna{should the y-axes on this and the below fig match? i.e. both be number of selected snps, or both be lambda indices?}\\
\anna{Try number of snps selected for x-axis, keep y-axis as precision}\\
\anna{Also why is pc-lasso doing so terribly? \textbf{depends on how you're defining precision... selects a lot of true snps but often they have the wrong sign}}\\

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pc1_corr.png}
\caption{Pathwise absolute correlation of selected, non-causal SNPs with the first principal component (PC1) of the data in Empirical genome-wide analysis. Plotted line is the mean absolute correlation of all incorrectly selected SNPs for a particular $\lambda$ value, with shaded region indicating SE bounds. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_pc1_corr}
\end{figure}
\anna{Should y-axis here be \# of selected snps to match above fig?}
